\huge A Better (One-Line!) Title Here

### 2016-10-19 pets2017-paper/pets2017-paper.tex
delete marker, since now sections todo and revise are color coded
hack at eval, and the two usability testing sections.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		LINDA'S PASS UP TO HERE 		       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Qualitative User Testing}
{\color {red}
\label{sec:qualitative}
We ran a qualitative, exploratory user study to gain an 
understanding of how users interact with the configuration interface and
what common problems may be. We did this by observing participants using 
the interface to circumvent censorship and interviewing them about
their experience.  Our observations during this study guided us in
redesigning the interface and provided hypotheses to test in our quantitative study.

\subsection{Recruitment}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 16 participants across the three censorship environments:
5~in E1, 5~in E2, and 6~in E3.
We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simulated censorship environment for our summative
usability test~\cite{summative}.

@@

{\color {blue}
Justification of quantitative analysis over qualitative.

Below are the empirical and criteria we use to assess the interfaces:  
\begin{itemize}
\item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition. This measures how many users are able to configure their connections with the interface. 
\item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap. This measures how much time is required for a user to connect to the Tor network. 
\item {\bfseries Active configuration time:} how much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap. This measures how much of the time spent connecting to the Tor network was spent configuring versus waiting. 
\end{itemize}

Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long. 
}

\section{Quantitative User Testing}
\label{sec:quantitative}

{\color {red} 
Having identified problems with the existing interface
and made changes to ameliorate them,
we quantify the existing problems
and the impact of our changes with a study involving a larger number of users.
We split participants by simulated censorship environments,
and between old and new interfaces.

\subsection{Setup}
We ran our experiment at <redacted>.
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
<redacted> %Xlab 
has 36 Windows~7 laptops, separated by cubicle walls. 
Though Tor Browser runs on other operating systems,
testing was only done on Windows, as a byproduct of using <redacted>. %Xlab.

>>>>

@@

{\color {blue}
It is easy to specify usability metrics, but hard to collect them. Typically, usability is measured relative to users' performance on a given set of test tasks. The most basic measures are based on the definition of usability as a quality metric: success rate (whether users can perform the task at all), the time a task requires, the error rate, and users' subjective satisfaction.
%https://www.nngroup.com/articles/usability-metrics/
%http://www.measuringu.com/blog/essential-metrics.php

We chose to evaluate the two interfaces by testing them on a large number of users, using the following criteria to measure usability: \\
\begin{itemize}
\item {\bfseries Success rate:} what percentage of users eventually connect to Tor in a given condition. 
\item {\bfseries Error rate:} what percentage of user attempts could not connect to Tor. 
\item {\bfseries Connection time:} time from Tor Browser startup to the first successful Tor bootstrap. 
\item {\bfseries Configuration time:} time from Tor Browser startup to progress screen, measures includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
\end{itemize}

Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long.

}

\section{Formative Usability Testing}
\label{sec:qualitative}
{\color {blue}
Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable. It is typically called a Formative Usability Evaluation. In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores. Summative tells you how usable an interface is and formative tells you what isn't usable.

Formative usability testing takes the role of a support tool for decision making during the beginning stages of the design process and - if applied early in the development process - provides valuable insights of where users have difficulty reaching their user goals with the technology (website, desktop GUI design, hardware product) or service.

With formative user testing, it is enough to test 3–5 users. After the fifth user tests, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again. Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.
%https://www.nngroup.com/articles/usability-metrics/
%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/
}

{\color {red}
\subsection{Recruitment}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 16 participants across the three censorship environments:
5~in E1, 5~in E2, and 6~in E3.
We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simulated censorship environment for our summative
usability test~\cite{summative}.

@@

\section{Summative Usability Testing}
\label{sec:quantitative}

{\color {blue} 
Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable. It is typically called a Formative Usability Evaluation. In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores. Summative tells you how usable an interface is and formative tells you what isn't usable.

Summative usability testing is a Quality Assurance (QA) type of test usually performed later in the development process. A similar usability test protocol is used as in formative usability testing but now this setup is used to do formal user acceptance testing before the product is released to the target audience. This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.

https://www.nngroup.com/articles/usability-metrics/
https://www.nngroup.com/articles/quantitative-studies-how-many-users/
}

{\color {red} 
\subsection{Setup}
We ran our experiment at <redacted>.
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
<redacted> %Xlab 
has 36 Windows~7 laptops, separated by cubicle walls. 
Though Tor Browser runs on other operating systems,
testing was only done on Windows, as a byproduct of using <redacted>. %Xlab.
